Gravitational Lens Recovery with \Glass: Illustrating the power of free-form lens modelling

### 2013-06-11 limits/ms.tex
New plots for results, mock galaxies, and sample reconstruction.
Removed unnecessary commented text and updated main results plots to include split plots for AC and BC mock galaxies.
added points to be emphasized
Justin's made a start. Abstract outline written. Very rough draft intro that still needs references. Will carry on through the rest of the paper tomorrow then add some polish in a second sweep. Hope everyone is happy so far.

\documentclass[onecolumn,galley]{mn2e}
%\documentclass[twocolumn,galley]{mn2e}
%\documentclass[onecolumn,galley,draft]{mn2e}
%\usepackage{myaasmacros}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{graphicx}

@@

%\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
\title[GLASS]{Lens Recovery with GLASS: An Extensible Free-Form Gravitational Lens Modeling Framework}
\author{%
Jonathan P. Coles 
\and 
Justin I. Read
\and 
Prasenjit Saha 
}

@@

\begin{abstract}
We show the effectiveness of reconstructing the mass distribution of four mock galaxies using
a range of strong gravitational lensing assumptions. In particular, we study
the affects of the lens morphology (double or quad) with and without a central
image, angular image distribution, and red shift contrast between two sources.
The lens modeling is performed using a new free-form framework called \Glass.
We conclude that \dots
%1) Time delays are unnecessary with strong red shift contrast,
%2)

%We study the effectiveness of a variety of strong lensing scenarios to inform
%the reconstruction of four simulated triaxial halos with stellar and dark
%matter components. We conclude that 
%1) lenses with multiple sources and high redshift contrast perform very well
%2) lenses where the images are already probing the stellar dominated region 
%   of a galaxy can be constrained by an estimate of the stellar mass and
%   suggest the fraction of dark matter
%3) if velocity dispersion measurements are to be used then a sufficiently large aperture 
%   is necessary
%4) lensing can be used to infer the velocity anisotropy.
%We also introduce GLASS, an extensible framework for lens modeling and analysis.

%We attempt to reconstruct the mass profile and distribution of a dark and
%stellar matter triaxial halo using a variety of strong lens configurations,
%stellar mass estimates, and stellar velocity dispersions. The lens
%configurations test quads with small to large image separations (radial
%sampling), extended source information ranging from point images to Einstein
%rings (angular sampling), and multiple sources located at the same and
%differing redshifts (redshift contrast).

%We conclude that redshift contrast can significantly constrain the mass
%profiles.  Stellar mass estimates can also lead to better reconstructions by
%placing lower bounds on the mass distribution in the inner regions of galaxies.
%Velocity dispersions alone are unlikely to usefully constrain the profile
%because the profile is highly sensitive to the dispersion measurement.  
%Combined with other techniques, however, velocity dispersions can help to
%constrain the range of possible reconstructed solutions. We also introduce
%GLASS, an extensible framework for lens modeling and analysis.  
\end{abstract}

@@

To date only about 400 strong lenses are known, but within the next ten years
new surveys will discover thousands of gravitational lenses. The SKA estimates
that after its start in 2020 about 10,000 lenses will be found. The LSST
expects to find about 5,000 multiply-imaged galaxies and about 150 AGNs or
quasar lenses after 2022.

A typical lens, where only the measured observables are the image positions,
can been used to estimate the total mass of a galaxy including parts of the
dark matter halo. The enclosed mass inside the Einstein radius is simple to
calculate and quite robust given the observed image positions. The exact mass
distribution is more difficult to determine, however, as there are typically
not enough constraints on the mass profile. The known degeneracies have been
discussed at length in the literature. At the very least, one would like to
have a measure of the enclosed mass at two distinct radii to be able
to properly distinguish between analytic mass models. 
%This would break the steepness degeneracy, also known as the mass sheet degeneracy.

Lensing is not the only technique that can measure enclosed mass. The enclosed
mass can also be estimated from stellar velocity dispersions. If the radius
from this measurement is sufficiently different from the Einstein radius, then
combining this measurement with lensing provides the necessary constraint.
Another solution is to find a galaxy that is lensing two sources. The images
from each source provide an enclosed mass. The extent to which the radii
differ is dependent upon the redshifts of the two sources: the larger the
redshift difference the larger the radial separation.

Lensing is known to be sensitive to cosmology and, in principle, can be used to
estimate such quantities as the Hubble constant $H_0$ when the lens has
measurable time delays. However, due to strong degeneracies such as the
steepness degeneracy there is often little one can learn from a single lens. 
In this case, one is free to change the mass and $H_0$ while keeping
all observables fixed. A single lens can say almost nothing about the actual
value of $H_0$. However, it has been shown that combining modeling results
of several strong lenses with time delays can significantly reduce the allowed
values and provides a measure to within 10 percent \cite{}.

If one assumes a Hubble constant $H_0$ and time delays have been observed for a
lens this will break the steepness degeneracy but will not help in
constraining the mass profile at two radii.  One can choose to postpone this
problem and simply fit models to the given data.  The earliest examples were
singular isothermal sphere (SIS) or elliptical (SIE) models but have since
evolved to multi-component models include separate models for the stars and
dark matter. Other methods that do not ignore this problem use genetic
algorithms or linear programming to explore the large space of solutions.

Despite such difficulties lensing is a direct probe of the gravitating mass in
a halo and there are a number of open problems in galaxy formation that lensing
can help address. For instance, the debate remains as to what form the inner
slope of the density profile takes. Numerical simulations of dark matter
suggest a cusp, while observations from lensing and stellar dynamics suggest
cores. This may, however, be only a matter of scale, as both theory and
observations agree that clusters have cuspy profiles.

Lensing may also be useful in measuring possible adiabatic contraction of the 
dark matter halo due to the central stars in a galaxy. For this, one needs
high resolution mass models of the stellar profile combined with accurate models
of the total mass. Indeed, with such models, one may also improve the statistics
of the dark matter fraction in a galaxies over many different mass scales.

These open problems suggest what kind of lensing data will be required in the
future.  Future surveys will provide many lenses but time delays will require a
long follow up. Stellar mass maps, however, take a known, fixed observation
time and can be performed for many lenses. It will be important not only to
measure the stellar velocity dispersion at an arbitrary radius, but to ensure
that the measurement is taken at a radius different to the Einstein radius.
For the radio surveys like SKA it will be important to detect the central image
of the lens. This can provide mass information all the way to the center of the
galaxy.

In this paper we perform a parameter study using four mock galaxies that differ
in their dark matter and stellar profiles. We consider double and quad lensing
morphologies, time delays, the presence of a central image, red shift contrast
between multiple sources, and image configuration.  We also consider the
effects of adding stellar mass models as lower bound constraints on the mass
distribution.  The modeling and analysis is performed using a new free form
lens modeling framework called \Glass.

We first review the basic lensing theory we will need and then describe how
\Glass is used to generate lensing models. The mock data and how it was
generated is described in \secref{}. In section{} we discuss the lensing
configurations in the parameter study and present some example output. Our
finals results are presented in \secref{}.

@@

\begin{figure}
%\plotone{AAZContrastR1R5_Tm.pdf}
\plotone{BCQuadR1a_TmS.pdf}
\caption{A typical reconstructed lens. Here we present a single quad lens from 
the BC mock galaxy.
\textbf{(Left)}
The arrival time surface. 
\textbf{(Middle)}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The green vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{(Right)}
The cumulative mass.}
\label{reconstruction}
\end{figure}

@@

\begin{figure}
%\plotone{AAarrival_surfaces}
%\plotone{BBarrival_surfaces}
\plotone{BCarrival_surfaces}
\caption{The lens configurations for the six test cases using the BC mock galaxy. Here,
the central image is shown, although not all tests include it. The central image belongs
to only one set of images to avoid overconstraining the models. Similar colors group
images that share a common source. In the case of the extended image systems the source
is at the same redshift, while the redshift is varied between the systems in the 
ZConstrast cases. Grey circles are a visual aid to help determine radial separation
between images. The axes are measure in arcseconds.}
\label{reconstruction}
\end{figure}

@@

%\tabref{Test configurations} summarizes how each of the configurations is composed.  
%\figref{Test reconstructions} shows the reconstructed lens.

%\subsection{Recovery} %--------------------------------------------------------------

%\begin{table}
%\begin{tabular}{lccccc}
%Source name & $z$ & $\beta$ & Image & $\vec\theta$ & $\Delta t$ (days) \\
%\hline
%AASingleSourceR1a & 1.72 & -0.59, 0.10 & A & -2.64, 5.07 & \\
% & & & B & -3.15, -4.62 & 37.09\\
% & & & C & -5.72, -0.67 & 33.58\\
% & & & D & 4.26, -0.20 & 259.75\\
% & & & E & 0.22, -0.02 & 104.48\\
%AASingleSourceR1b & 1.72 & 0.11, -0.46 & A & 0.49, -5.85 & \\
% & & & B & 0.87, 4.91 & 228.69\\
% & & & C & 4.80, 1.57 & 31.83\\
% & & & D & -4.58, 1.40 & 56.15\\
% & & & E & -0.09, 0.11 & 180.09\\
%AAExtendedSourceR1a & 1.72 & -0.23, -0.13 & A & -1.08, -5.48 & \\
% & & & B & -1.26, 5.19 & 66.27\\
% & & & C & -5.31, 0.49 & 74.72\\
% & & & D & 4.72, 0.33 & 99.26\\
% & & & E & 0.04, 0.02 & 174.11\\
%AAExtendedSourceR1b & 1.72 & -0.37, 0.04 & A & -1.73, 5.27 & \\
% & & & B & -1.93, -5.13 & 14.76\\
% & & & C & -5.53, -0.27 & 75.45\\
% & & & D & 4.56, -0.05 & 160.47\\
% & & & E & 0.09, -0.01 & 147.24\\
%AAExtendedSourceR1c & 1.72 & -0.62, -0.13 & A & -2.84, -5.01 & \\
% & & & B & -3.47, 4.36 & 60.96\\
% & & & C & -5.66, 0.92 & 17.14\\
% & & & D & 4.13, 0.23 & 270.45\\
% & & & E & 0.40, 0.06 & 83.81\\
%AASingleSourceR2 & 1.50 & 0.11, -0.46 & A & 0.49, -5.66 & \\
% & & & B & 0.98, 4.67 & 227.84\\
% & & & C & 4.48, 1.70 & 27.39\\
% & & & D & -4.34, 1.34 & 54.57\\
% & & & E & -0.12, 0.21 & 144.98\\
%AASingleSourceR3 & 1.00 & 0.11, -0.46 & A & 0.48, -5.05 & \\
% & & & B & 0.92, 3.98 & 226.30\\
% & & & C & 3.70, 1.67 & 19.74\\
% & & & D & -3.55, 1.20 & 53.34\\
% & & & E & -0.12, 0.15 & 96.33\\
%AASingleSourceR4 & 0.80 & 0.11, -0.46 & A & 0.39, -4.50 & \\
% & & & B & 0.93, 3.38 & 223.14\\
% & & & C & 2.98, 1.69 & 9.75\\
% & & & D & -2.82, 1.09 & 48.86\\
% & & & E & -0.15, 0.18 & 52.90\\
%AASingleSourceR5 & 0.72 & 0.11, -0.46 & A & 0.44, -4.22 & \\
% & & & B & 1.02, 2.94 & 219.75\\
% & & & C & 2.51, 1.69 & 4.63\\
% & & & D & -2.36, 1.03 & 44.24\\
% & & & E & -0.16, 0.20 & 32.56
%\end{tabular}
%\end{table}

@@

%\begin{figure}
%\plotone{AASingleQuadR1a_Tm.png}
%\caption{The reconstruction of AASingleQuadR1a\_Tm.}
%\end{figure}

%\begin{table}
%\begin{tabular}{lccccccc}
%Source name & $z$ & $\beta$ & $A$ (min) & $B$ (min) & $C$ (saddle) & $D$ (saddle) & $E$ (max)\\
%\hline
%SingleQuad1 & 2.50 & -0.37,0.08 & -2.40,10.40 & -2.55,-10.26 & -10.93,-0.39 & 10.37,-0.23 & 0.03,-0.01\\
%SingleQuad2 & 0.40 & 0.08,-0.51 & 0.32,-7.23 & 0.70,6.40 & 6.30,1.74 & -6.22,1.59 & -0.03,0.08\\
%SingleQuad3 & 0.60 & 0.08,-0.51 & 0.27,-8.86 & 0.74,8.08 & 8.13,1.93 & -8.05,1.72 & -0.03,0.06\\
%SingleQuad4 & 0.80 & 0.08,-0.51 & 0.36,-9.58 & 0.70,8.82 & 8.92,2.05 & -8.87,1.76 & -0.02,0.05\\
%SingleQuad5 & 1.00 & 0.08,-0.51 & 0.38,-10.00 & 0.68,9.24 & 9.40,1.99 & -9.34,1.79 & -0.02,0.05\\
%ExtendedSource0 & 0.40 & 0.20,0.57 & 0.79,7.25 & 1.51,-6.25 & 6.29,-2.07 & -6.12,-1.55 & -0.06,-0.08\\
%ExtendedSource1 & 0.40 & -0.15,0.17 & -0.64,6.96 & -0.84,-6.66 & -6.67,-0.56 & 6.39,-0.52 & 0.02,-0.03\\
%ExtendedSource2 & 0.40 & 0.06,-0.33 & 0.24,-7.09 & 0.44,6.56 & 6.47,1.18 & -6.43,0.98 & -0.03,0.05
%\end{tabular}
%\caption{Source data.}
%\label{source data}
%\end{table}
%
%\begin{table}
%\begin{tabular}{lrrrr}
%Source name & $\Delta t_{AB}$ & $\Delta t_{BC}$ & $\Delta t_{CD}$ & $\Delta t_{DE}$\\
%\hline
%SingleQuad1 & 38.97 & 171.07 & 207.10 & 1314.05\\
%SingleQuad2 & 335.01 & 97.91 & 50.78 & 623.95\\
%SingleQuad3 & 312.86 & 122.63 & 47.83 & 951.56\\
%SingleQuad4 & 303.39 & 128.81 & 46.63 & 1102.50\\
%SingleQuad5 & 298.27 & 131.32 & 45.70 & 1188.64\\
%ExtendedSource0 & 360.17 & 62.16 & 115.30 & 588.15\\
%ExtendedSource1 & 109.28 & 169.77 & 91.20 & 620.78\\
%ExtendedSource2 & 217.40 & 148.57 & 36.52 & 642.27
%\end{tabular}
%\caption{Time delays for each image system.}
%\label{source time delays}
%\end{table}
%
%\begin{table}
%\begin{tabular}{ll}
%\label{test systems}
%Test name & Source name\\
%\hline
%SingleQuad & SingleQuad1\\
%SingleQuad2 & SingleQuad2\\
%ExtendedSource & ExtendedSource0 + ExtendedSource1 + ExtendedSource2\\
%ZContrastDoubleQuad0 & SingleQuad1 + SingleQuad2\\
%ZContrastDoubleQuad1 & SingleQuad1 + SingleQuad3\\
%ZContrastDoubleQuad2 & SingleQuad1 + SingleQuad4\\
%ZContrastDoubleQuad3 & SingleQuad1 + SingleQuad5
%\end{tabular}
%\caption{Test configurations}
%\label{Test configurations}
%\end{table}

@@

%\subsection{Model quality}

@@

%\begin{figure}
%\label{chi2}
%\plottwo{AAchi2_profile.pdf}{AAchi2_profile.pdf} \\
%\plottwo{BBchi2_profile.pdf}{BCchi2_profile.pdf}
%\caption{
%Goodness of fit plots for the reconstruction of each of the four galaxies given
%the different lensing test cases. The $\chi^2$ is computed over the radial $\kappa$
%profile with data points at the median value and the error bars showing the 68\% confidence
%interval.
%}
%\end{figure}

%\begin{figure}
%\plotone{SingleQuad_TmC.png}
%\caption{SingleQuad}
%\label{SingleQuad}
%\end{figure}
%
%\begin{figure}
%\plotone{SingleQuad2_TmC.png}
%\caption{SingleQuad2}
%\label{SingleQuad2}
%\end{figure}
%
%\figref{SingleQuad}
%\figref{SingleQuad2}
%
%\begin{figure}
%\plotone{ExtendedSource_TmC.png}
%\caption{ExtendedSource}.
%\label{ExtendedSource}
%\end{figure}
%
%\figref{ExtendedSource}
%
%\begin{figure}
%\plotone{ZContrastDoubleQuad0_TmC.png}
%\caption{ZContrastDoubleQuad0}
%\label{ZContrastDoubleQuad0}
%\end{figure}
%
%\begin{figure}
%\plotone{ZContrastDoubleQuad1_TmC.png}
%\caption{ZContrastDoubleQuad1}
%\label{ZContrastDoubleQuad1}
%\end{figure}
%
%\begin{figure}
%\plotone{ZContrastDoubleQuad2_TmC.png}
%\caption{ZContrastDoubleQuad2}
%\label{ZContrastDoubleQuad2}
%\end{figure}
%
%\begin{figure}
%\plotone{ZContrastDoubleQuad3_TmC.png}
%\caption{ZContrastDoubleQuad3}
%\label{ZContrastDoubleQuad3}
%\end{figure}
%
%\figref{ZContrastDoubleQuad0}
%\figref{ZContrastDoubleQuad1}
%\figref{ZContrastDoubleQuad2}
%\figref{ZContrastDoubleQuad3}

%\subsection{Aperture}

%\begin{figure}
%\plotone{sigma_beta.pdf}
%\caption{}
%\end{figure}

\section{Discussion} %--------------------------------------------------------------

%\begin{figure}
%\plotone{SingleQuad_Tmc_eig.png}
%\plotone{SingleQuad2_Tmc_eig.png}
%\plotone{ExtendedSource_Tmc_eig.png}
%\plotone{ZContrastDoubleQuad0_Tmc_eig.png}
%\plotone{ZContrastDoubleQuad1_Tmc_eig.png}
%\plotone{ZContrastDoubleQuad2_Tmc_eig.png}
%\plotone{ZContrastDoubleQuad3_Tmc_eig.png}
%\end{figure}

@@

%\section{Choice of modeling parameters}
%
%
%\begin{itemize}
%\item \figref{raytracing convergence tests}
%\item Why do we choose {\texttt maprad}=20 arcsec when generating test cases?
%We need to enclose most of the mass for the time delays to be stable.  
%\item Why do we choose {\texttt pixrad}=45 when generating the test cases? We
%need sufficient resolution for the image positions to be stable.  
%\end{itemize}

%\section{GLASS - An Extensible Gravitational Lens Modeling Framework}
%\label{GLASS Description}
%\begin{itemize} 
%\item Framework that incorporates lens modeling, analysis, and plotting.
%\item Not limited to just pixels based modeling. Can be used with functional forms like Bessel functions. Not yet implemented.
%\item Allows for post processing and criteria matching on a per model basis.
%\item Input files are python programs but from within the framework that aspect may be ignored.
%
%\item Lens reconstruction. Based on PixeLens. Express data constraints and
%priors as linear equations. Sample the resulting simplex.
%\item Standard data constraints: image positions, time delays, hubble constant, parity, annular density, external shear.
%\item Priors: range of profile steepness, local gradient, smoothness, shared H0, symmetry for doubles.
%\item Local gradient and smoothness are now convergent. Based on physical size rather than number of neighbors.
%
%\item Raytracing. Use a fine grid to sample the 2d function mapping position on
%the image plane to distance from the source on the source plane. From those
%points that are near the source, use a 2d root finder to locate the exact
%positions. Merge nearly identical solutions.

%\end{itemize}

>>>>

\documentclass[galley]{mn2e}
%\documentclass[twocolumn,galley]{mn2e}
%\documentclass[onecolumn,galley,draft]{mn2e}
%\usepackage{myaasmacros}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{graphicx}

@@

%\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
\title[\Glass]{Gravitational Lens Recovery with \Glass: Illustrating the power of free-form lens modelling}
\author{%
Jonathan P. Coles 
\and 
Justin I. Read
\and 
Prasenjit Saha 
}

@@

\begin{abstract}
{\bf JR. Does \Glass\ stand for something?}\\
We introduce a new free-form gravitational lens modelling tool \Glass\ that builds on an earlier code \PixeLens. Like \PixeLens, we use a grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties. However, \Glass\ improves on \PixeLens\ in a number of important respects: (i) it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors; (ii) it is built on a fully modular framework that can support different basis functions; (iii) non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented); (iv) the stellar mass (if known) can be applied as a prior; and (v) adaptive resolution can be used in regions of interest. We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data are required to  measure the circularly averaged mass profile of a lens and its shape. We find that for pure lens data, multiple sources with wide redshift separation give the strongest constraints as this breaks the well-known mass-sheet or steepness degeneracy. However, a single quad with time delays also performs well. Folding in additional constraints from stellar population synthesis modelling provides powerful additional constraints for galaxy lenses where the stars dominate the central potential, providing similarly good constraints from a single double without time delays as a quad with time delays in the absence of stellar mass constraints. Stellar kinematic data is only useful for probing the mass profile within the half light radius $r_{1/2}$ of the stars provided data are available for $r \gg r_{1/2}$ since this is required to integrate out the unknown velocity anisotropy $\beta(r)$. On the other hand, if the lensing data already probe the mass profile over the region $r \sim r_{1/2}$, then stellar kinematic data can be used to probe $\beta(r)$ -- an interesting dynamic quantity in its own right. Where information on the mass distribution from lensing and other probes becomes redundant, this opens up the possibility of using strong lensing to probe cosmology. We will study this, and present the first results from \Glass\ applied to real data, in forthcoming papers.
\end{abstract}

@@

Since the discovery of the first gravitational lens (CITE), lensing has become an increasingly important probe of the distribution of mass in the Universe (CITE). Strong lensing in particular provides a powerful probe of the mass distribution at the heart of galaxies and galaxy clusters given good enough data (CITE). This in turn provides valuable constraints on the nature of dark matter (CITE), on cosmological models (CITE), and on galaxy formation models (CITE). To date, some $\sim$400 strong lenses are known (CITE), but with the advent of large ground and space based surveys, this number is set to explode, with thousands of lenses expected to be discovered over the next ten years (CITE).

The majority of lens modelling efforts to date have focussed on `parametric' modelling, where simple theoretically motived models are fit using maximum likelihood methods to the data (CITE). This is useful in that a simple model provides valuable physical insight (CITE). However, as data quality improves and the questions we ask of these data become more refined, it is important to re-asses the impact of our model assumptions. `Non-parameteric' methods -- that assume many more parameters than the available data constraints -- are invaluable in this respect. In non-parametric mass modelling, the lens inversion problem is deliberately chosen to be under-constrained (CITE). Instead of finding one `best-fit' model, we must search for many models consistent with the data, exploring degeneracies between different but plausible mass models. This latter word -- {\it plausible} -- encodes the key hidden gremlin in non-parametric methods: constraints extra to the available data are typically required on the solution space in order to make it finite -- priors (CITE). However, even rather restrictive priors are far less restrictive than the implicit constraints inherent in parametric mass modelling. The key advantages of non-parametric modelling are that we can: (i) explore model degeneracies and marginalise over them; and (ii) we can determine what type and quality of data (including addition non-lensing data) are required to measure parameters of interest.

In this paper, we present a new free-form or `non-parametric' strong lens modelling framework \Glass\ that builds on an earlier code \PixeLens (CITE). Like \PixeLens, we use a grid of mass pixels to model the lens, searching through many models consistent with the data to marginalise over model uncertainties. However, \Glass\ improves on \PixeLens\ in a number of important respects:

\begin{enumerate} 
\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors;
\item it is built on a fully modular framework that can support different basis functions;
\item non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented);
\item the stellar mass (if known) can be applied as a prior; and
\item adaptive resolution can be used in regions of interest. 
\end{enumerate}

We apply \Glass\ to a suite of dynamically realistic mock N-body data to determine what quality of data from strong lensing, stellar populations synthesis models and/or stellar kinematics are required to measure the circularly averaged mass profile of a lens and its shape. We will consider using strong lensing as a cosmological probe, and present the first results from \Glass\ applied to real data, in forthcoming papers.

%(The SKA estimates that after its start in 2020 about 10,000 lenses will be found. The LSST expects to find about 5,000 multiply-imaged galaxies and about 150 AGNs or quasar lenses after 2022.)

%A typical lens, where only the measured observables are the image positions, can been used to estimate the total mass of a galaxy including parts of the dark matter halo. The enclosed mass inside the Einstein radius is simple to calculate and quite robust given the observed image positions. The exact mass distribution is more difficult to determine, however, as there are typically not enough constraints on the mass profile. The known degeneracies have been discussed at length in the literature. At the very least, one would like to have a measure of the enclosed mass at two distinct radii to be able to properly distinguish between analytic mass models. This would break the steepness degeneracy, also known as the mass sheet degeneracy.

%Lensing is not the only technique that can measure enclosed mass. The enclosed mass can also be estimated from stellar velocity dispersions. If the radius from this measurement is sufficiently different from the Einstein radius, then combining this measurement with lensing provides the necessary constraint. Another solution is to find a galaxy that is lensing two sources. The images from each source provide an enclosed mass. The extent to which the radii differ is dependent upon the redshifts of the two sources: the larger the redshift difference the larger the radial separation.

%Lensing is known to be sensitive to cosmology and, in principle, can be used to estimate such quantities as the Hubble constant $H_0$ when the lens has measurable time delays. However, due to strong degeneracies such as the steepness degeneracy there is often little one can learn from a single lens. In this case, one is free to change the mass and $H_0$ while keeping all observables fixed. A single lens can say almost nothing about the actual value of $H_0$. However, it has been shown that combining modeling results of several strong lenses with time delays can significantly reduce the allowed values and provides a measure to within 10 percent \cite{}.

%If one assumes a Hubble constant $H_0$ and time delays have been observed for a lens this will break the steepness degeneracy but will not help in constraining the mass profile at two radii.  One can choose to postpone this problem and simply fit models to the given data.  The earliest examples were singular isothermal sphere (SIS) or elliptical (SIE) models but have since evolved to multi-component models include separate models for the stars and dark matter. Other methods that do not ignore this problem use genetic algorithms or linear programming to explore the large space of solutions.

%Despite such difficulties lensing is a direct probe of the gravitating mass in a halo and there are a number of open problems in galaxy formation that lensing can help address. For instance, the debate remains as to what form the inner slope of the density profile takes. Numerical simulations of dark matter suggest a cusp, while observations from lensing and stellar dynamics suggest cores. This may, however, be only a matter of scale, as both theory and observations agree that clusters have cuspy profiles.

%Lensing may also be useful in measuring possible adiabatic contraction of the dark matter halo due to the central stars in a galaxy. For this, one needs high resolution mass models of the stellar profile combined with accurate models of the total mass. Indeed, with such models, one may also improve the statistics of the dark matter fraction in a galaxies over many different mass scales.

%These open problems suggest what kind of lensing data will be required in thefuture.  Future surveys will provide many lenses but time delays will require a long follow up. Stellar mass maps, however, take a known, fixed observation time and can be performed for many lenses. It will be important not only to measure the stellar velocity dispersion at an arbitrary radius, but to ensure that the measurement is taken at a radius different to the Einstein radius. For the radio surveys like SKA it will be important to detect the central image of the lens. This can provide mass information all the way to the center of the galaxy.

This paper is organised as follows. We first review the basic lensing theory we will need and then describe how \Glass\ is used to generate lensing models. The mock data and how it was generated is described in \secref{}. In section{} we discuss the lensing configurations in the parameter study and present some example output. Our finals results are presented in \secref{}.

@@

\begin{figure}
\plotthree{BCQuadR1a_TmS-a.pdf}{BCQuadR1a_TmS-b.pdf}{BCQuadR1a_TmS-c.pdf}
\caption{A typical reconstructed lens. Here we present a single quad lens from 
the BC mock galaxy.
\textbf{(Left)}
The arrival time surface. 
\textbf{(Middle)}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The green vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{(Right)}
The cumulative mass.}
\label{reconstruction}
\end{figure}

@@

\begin{figure}
\plotone{BCarrival_surfaces}
\caption{The lens configurations for the six test cases using the BC mock galaxy. Here,
the central image is shown, although not all tests include it. The central image belongs
to only one set of images to avoid overconstraining the models. Similar colors group
images that share a common source. In the case of the extended image systems the source
is at the same redshift, while the redshift is varied between the systems in the 
ZConstrast cases. Grey circles are a visual aid to help determine radial separation
between images. The axes are measure in arcseconds.}
\label{reconstruction}
\end{figure}

@@

@@

@@

@@

\section{Discussion}

extensible framework

accurate reconstructions through better sampling

where stellar mass significant, including it greatly improves accuracy

breaking the vdisp/anisotropy degeneracy.

@@
